Dynamic strategies for yaw and induction control of wind farms based on large-eddy simulation and optimization

### 2018-01-02 MuntersMeyers_DynamicStrategiesControl_revision_WM01.tex
Fix typo

\subsubsection{Induction characteristics}\label{subsec:uni_induction}
\noindent Figure~\ref{fig:dynamic_ctfilt} illustrates the time evolution of normalized power extraction and thrust coefficient of the optimal induction cases (I2, I3, I2Y, and I3Y), as defined in Table~\ref{tab:case_definition}. In contrast to the heterogeneous behavior in different columns for the yaw angles as shown in Figure~\ref{fig:dynamic_uniform} above, the induction coefficient behavior is similar for each column, and is illustrated for column C1 only. The top panels of Figure~\ref{fig:dynamic_ctfilt} indicate that, for the exclusively inductive cases I2 and I3, first-row power is pulsed severely, leading to intermittent increases in downstream power extraction. This differs from the combined yaw--induction cases, which show much smoother power extraction dynamics. 
\begin{figure}
	\includegraphics[width=\textwidth]{figure10}	
	\caption{Time evolution of column C1 in uniform inflow induction-enabled cases. \emph{Top: } Turbine power extraction $P$, normalized by mean first row power in the uncontrolled reference $\overline{P}_{R1}^R$. \emph{Bottom: } Thrust coefficient $\widehat{C}_T'$. \label{fig:dynamic_ctfilt}}
\end{figure}

>>>>

\subsubsection{Induction characteristics}\label{subsec:uni_induction}
\noindent Figure~\ref{fig:dynamic_ctfilt} illustrates the time evolution of normalized power extraction and thrust coefficient of the optimal induction cases (I2, I3, I2Y, and I3Y), as defined in Table~\ref{tab:case_definition}. In contrast to the heterogeneous behavior in different columns for the yaw angles as shown in Figure~\ref{fig:dynamic_uniform} above, the induction coefficient behavior is similar for each column, and is illustrated for column C1 only. The top panels of Figure~\ref{fig:dynamic_ctfilt} indicates that, for the exclusively inductive cases I2 and I3, first-row power is pulsed severely, leading to intermittent increases in downstream power extraction. This differs from the combined yaw--induction cases, which show much smoother power extraction dynamics. 
\begin{figure}
	\includegraphics[width=\textwidth]{figure10}	
	\caption{Time evolution of column C1 in uniform inflow induction-enabled cases. \emph{Top: } Turbine power extraction $P$, normalized by mean first row power in the uncontrolled reference $\overline{P}_{R1}^R$. \emph{Bottom: } Thrust coefficient $\widehat{C}_T'$. \label{fig:dynamic_ctfilt}}
\end{figure}
